% Template for ICASSP-2013 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
%\documentclass[conferen\overlinece]{IEEEtran}
%\documentclass[journal]{IEEEtran}
\usepackage{amssymb,bm}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{appendix}
\usepackage{hyperref}
\usepackage{authblk}
\usepackage{color}


\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

%\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem*{cor}{Corollary}
\newtheorem{alg}[thm]{Algorithm}
\newtheorem{assu}[thm]{Assumption}

%\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\newtheorem{conj}{Conjecture}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{app}{Application}
\newtheorem{prob}{Problem}
\newtheorem{pf}{Proof}

\theoremstyle{remark}
\newtheorem{rem}{Remark}

\usepackage{graphics}
\usepackage{graphicx,subcaption}
\usepackage{algorithm}
\usepackage{algorithmic}
% \usepackage[colorlinks,linkcolor=red,citecolor=black]{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}

%\usepackage[english]{babel}

\usepackage{cite}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}

%%%%%%%%%% TABLE package %%%%%%%%%%%%%
\usepackage{threeparttable}
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}
\def\var{\rm{var}}
%\renewcommand{\arraystretch}{2.0}

%%%%%%%%%% Figure %%%%%%%%%%%%%%%%
\floatstyle{plain}
\restylefloat{figure}
\usepackage{placeins}
\def\diag{\rm{diag}}
\newcommand{\mbR}{\mathbb{R}}

%\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
%\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
%\newcommand{\pushline}{\Indp}% Indent
%\newcommand{\popline}{\Indm\dosemic}% Undent

%\usepackage[dvipdfm]{hyperref}

%\usepackage{fancyheadings}
%\pagestyle{fancy}
%\lhead{page \thepage}
% \chead{By J. Yi on \today, jirong-yi@uiowa.edu}
%\rhead{\ }
\renewcommand{\baselinestretch}{1.0}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\y{{\mathbf y}}
\def\cov{\rm{cov}}
%\def\L{{\cal L}}

\newcommand{\bSigma}{{\boldsymbol \Sigma}}
\newcommand{\bOmega}{{\boldsymbol \Omega}}
\newcommand{\bbeta}{{\boldsymbol \beta}}
\newcommand{\bepsilon}{{\boldsymbol \epsilon}}
\newcommand{\bA}{{\boldsymbol A}}
\newcommand{\bB}{{\boldsymbol B}}
\newcommand{\bC}{{\boldsymbol C}}
\newcommand{\bD}{{\boldsymbol D}}
\newcommand{\bE}{{\boldsymbol E}}
\newcommand{\bF}{{\boldsymbol E}}
\newcommand{\bG}{{\boldsymbol G}}
\newcommand{\bH}{{\boldsymbol H}}
\newcommand{\bI}{{\boldsymbol I}}
\newcommand{\bJ}{{\boldsymbol J}}
\newcommand{\bM}{{\boldsymbol M}}
\newcommand{\bN}{{\boldsymbol N}}
\newcommand{\bP}{{\boldsymbol P}}
\newcommand{\bQ}{{\boldsymbol Q}}
\newcommand{\bR}{{\boldsymbol R}}
\newcommand{\bS}{{\boldsymbol S}}
\newcommand{\bT}{{\boldsymbol T}}
\newcommand{\bU}{{\boldsymbol U}}
\newcommand{\bV}{{\boldsymbol V}}
\newcommand{\bW}{{\boldsymbol W}}
\newcommand{\bX}{{\boldsymbol X}}
\newcommand{\bY}{{\boldsymbol Y}}
\newcommand{\bZ}{{\boldsymbol Z}}
\newcommand{\bRA}{{\boldsymbol {RA}}}

\newcommand{\ba}{{\boldsymbol a}}
\newcommand{\bb}{{\boldsymbol b}}
\newcommand{\bc}{{\boldsymbol c}}
\newcommand{\bd}{{\boldsymbol d}}
\newcommand{\be}{{\boldsymbol e}}
\newcommand{\f}{{\boldsymbol f}}
\newcommand{\bg}{{\boldsymbol g}}
\newcommand{\bh}{{\boldsymbol h}}
\newcommand{\bn}{{\boldsymbol n}}
\newcommand{\bp}{{\boldsymbol p}}
\newcommand{\bq}{{\boldsymbol q}}
\newcommand{\bu}{{\boldsymbol u}}
\newcommand{\bv}{{\boldsymbol v}}
\newcommand{\bw}{{\boldsymbol w}}
\newcommand{\bx}{{\boldsymbol x}}
\newcommand{\bs}{{\boldsymbol s}}
\newcommand{\by}{{\boldsymbol y}}
\newcommand{\bz}{{\boldsymbol z}}


\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\newcommand{\C}{{\mathbb C}}
\newcommand{\ind}{{\mathbb I}}
\newcommand{\Pb}{{\mathbb P}}

\newcommand{\cTheta}{{\mathcal{\Theta}}}
\newcommand{\cA}{{\mathcal{A}}}
\newcommand{\cP}{{\mathcal{P}}}
\newcommand{\cD}{{\mathcal{D}}}
\newcommand{\cR}{{\mathcal{R}}}
\newcommand{\cH}{{\mathcal{H}}}
\newcommand{\cI}{{\mathcal{I}}}
\newcommand{\cN}{{\mathcal{N}}}
\newcommand{\cG}{{\mathcal{G}}}
\newcommand{\cT}{{\mathcal{T}}}
\newcommand{\cQ}{{\mathcal{Q}}}
\newcommand{\cS}{{\mathcal S}}
\newcommand{\cE}{{\mathcal E}}
\newcommand{\cX}{{\boldsymbol {\mathcal X}}}
\newcommand{\cL}{\mathcal L}
\newcommand{\cW}{{\boldsymbol {\mathcal W}}}


\newcommand{\grad}{{\nabla}}
\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\newcommand{\argmin}{\mathrm{argmin}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\sgn}{\mathrm{sgn}}


% Title.
% ------
\begin{document}

\title{Sensing Matrix Design}

\author{
Jirong Yi {\footnote{
Department of Electrical and Computer Engineering, University of Iowa, Iowa City, IA 52242. Corresponding email: jirong-yi@uiowa.edu.}}\,}\,


%\textsuperscript{c}\thanks{\noindent\textsuperscript{c}Department of Electrical and Computer Engineering, University of Iowa, Iowa City, IA 52242. \\
%Email: \texttt{weiyu-xu@uiowa.edu}}
%}

\maketitle

\section{A quick start}\label{Sec:QuickStart}

Follow the following steps to start the system

\begin{itemize}
\item Run the file start\_PTS\_cmpct.m in MATLAB (preferably MATLAB versions no earlier than 2014b)

\item In the ``Pooling Matrix Design (PMD)'' panel, first select the pooling matrix size by click on the pop-up menu, and then click on the ``Generate Pooling Matrix'' button. Finally click on the ``Next Step: Entering Pooling Results (EPR)'' button. 

\item In the ``Entering Pooling Results (EPR)'' panel, click on the ``Start New'' button, and then enter the pooling results to the table in the panel, and click the ``Finish'' button. Finally click on the ``Next Step: Sample Results Decoding (SRD)''. 

\item In the ``Sample Results Decoding (SRD)'' panel, the decoded sample results can be reviewed. 
\end{itemize}

Supplemental functionalities

\begin{itemize}
\item In the ``Entering Pooling Results (EPR)'' step, enter multiple groups of pooling results by simply repeating the following process before clicking on ``Next Step: Sample Results Decoding (SRD)'': click the ``Start New'' button, and then enter the next group of pooling results, and then click on the ``Finish'' button.

\item In the ``Entering Pooling Results (EPR)'' step, review the previous group of pooling results entered by click on the ``Previous'' button, and review the next group of pooling results entered by click on the ``Next'' button.

\item In the ``Sample Results Decoding (SRD)'' step, review the decoding results of the previous group of pooling results entered by click on the ``Previous'' button, and review the decoding results of the next group of pooling results entered by click on the ``Next'' button.

\item In the ``Sample Results Decoding (SRD)'' step, click on the ``Save'' button to save data. 

\item In the ``Sample Results Decoding (SRD)'' panel, 

\end{itemize}

Warnings

\begin{itemize}

\item The pooling results used as user input in ``Entering Pooling Results (EPR)'' step should be obtained via the corresponding pooling matrix obtained in ``Pooling Matrix Design (PMD)'' step.

\item Every time the user generates new pooling matrix, the ``Entering Pooling Results (EPR)'' and the ``Sample Results Decoding (SRD)'' will be reset to default status, and all the data will not be cleared up.

\item Every time the user enters new pooling results in the ``Entering Pooling Results (EPR)'' step, the ``Sample Results Decoding (SRD)'' step will be reset to default status.

\item The users are not allowed to modify the elements of the pooling matrix generated. 

\item The users are not allowed to modify the decoded sample results. 


\end{itemize}

\end{document}
